---
title: "Express STI Clinic Manuscript Plots"
output:
  pdf_document: default
  html_document: default
  word_document: default
classoption: landscape
---

## Benefits Line Graph: Prevalence ## 

```{r, echo=FALSE, warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(dev="png")

dat <- prev_all_weeks_both_scenario

dat[which(dat$Type == "prev.ugc"), "Type"] <- "Urogenital Infections"
dat[which(dat$Type == "prev.rgc"), "Type"] <- "Rectal Infections"
dat[which(dat$Type == "prev.ogc"), "Type"] <- "Pharyngeal Infections"
dat[which(dat$Type == "prev.gc"), "Type"] <- "Overall Cases"

# results w/ 95% confidence interval # TODO - is this correct?
dat_mean_conf_int <- ddply(dat, .(Week, Year, Type, Scenario), summarize, 
                           Mean =  mean_se(Value, mult = 1.96)$y,
                           Conf_Int_Lo = mean_se(Value, mult = 1.96)$ymin,
                           Conf_Int_Hi = mean_se(Value, mult = 1.96)$ymax)
      
ggplot(dat_mean_conf_int, aes(x = Week, y = Mean), alpha = 0.2) +
  geom_line(aes(color = Scenario)) +
  geom_ribbon(aes(fill = Scenario, ymin = Conf_Int_Lo, ymax = Conf_Int_Hi), alpha = 0.2) +
  facet_wrap(~Type, ncol = 2) +
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white"),
        panel.border = element_rect(color = "black", size = 0.1, fill = NA),  
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(size = 0.1, color = "grey"),
        panel.grid.major.y = element_line(size = 0.1, color = "grey"),
        axis.line = element_line(size = 0.1, linetype = "solid",
                                 color = "black"),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 10),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

# results w/ 89% credible interval # TODO - is this correct?
dat_mean_cred_int <- ddply(dat, .(Week, Year, Type, Scenario), summarize, 
                           Mean =  mean(Value),
                           Cred_Int_Lo = ci(Value, ci = 0.95)$CI_low,
                           Cred_Int_Hi = ci(Value, ci = 0.95)$CI_high)
      
ggplot(dat_mean_cred_int, aes(x = Week, y = Mean), alpha = 0.2) +
  geom_line(aes(color = Scenario)) +
  geom_ribbon(aes(fill = Scenario, ymin = Cred_Int_Lo, ymax = Cred_Int_Hi), alpha = 0.2) +
  facet_wrap(~Type, ncol = 2) +
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white"),
        panel.border = element_rect(color = "black", size = 0.1, fill = NA),  
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(size = 0.1, color = "grey"),
        panel.grid.major.y = element_line(size = 0.1, color = "grey"),
        axis.line = element_line(size = 0.1, linetype = "solid",
                                 color = "black"),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 10),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

# results w/ 89% credible interval # TODO - is this correct? From Minttu paper
dat_group <- group_by(dat, Week, Year, Type, Scenario) %>% 
  summarise(Mean = mean(Value, na.rm=T),
            ci_high = quantile(Value, 0.975, na.rm = T),
            ci_low = quantile(Value, 0.025, na.rm = T))

ggplot(dat_group, aes(x = Week, y = Mean), alpha = 0.2) +
  geom_line(aes(color = Scenario)) +
  geom_ribbon(aes(fill = Scenario, ymin = ci_low, ymax = ci_high), alpha = 0.2) +
  facet_wrap(~Type, ncol = 2) +
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white"),
        panel.border = element_rect(color = "black", size = 0.1, fill = NA),  
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(size = 0.1, color = "grey"),
        panel.grid.major.y = element_line(size = 0.1, color = "grey"),
        axis.line = element_line(size = 0.1, linetype = "solid",
                                 color = "black"),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 10),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))


```

## Benefits Line Graph: Incidence per 100 Person-Years ## 

```{r, echo=FALSE, warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(dev="png")

dat <- ir100_week_combo

dat[which(dat$Type == "ugc"), "Type"] <- "Urogenital Infections"
dat[which(dat$Type == "rgc"), "Type"] <- "Rectal Infections"
dat[which(dat$Type == "ogc"), "Type"] <- "Pharyngeal Infections"
dat[which(dat$Type == "gc"), "Type"] <- "Overall Cases"
  
dat_mean <- ddply(dat, .(Week, Type, Scenario), summarize, Mean = mean(Value))
b <- ggplot(dat_mean, aes(x = Week, y = Mean), alpha = 0.2)

b + geom_line(aes(color = Scenario)) + 
  facet_wrap(~Type, ncol = 2) +
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white"),
        panel.border = element_rect(color = "black", size = 0.1, fill = NA),  
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(size = 0.1, color = "grey"),
        panel.grid.major.y = element_line(size = 0.1, color = "grey"),
        axis.line = element_line(size = 0.1, linetype = "solid",
                                 color = "black"),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 10),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

b + geom_smooth(aes(color = Scenario)) +
  facet_wrap(~Type, ncol = 2) +
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white"),
        panel.border = element_rect(color = "black", size = 0.1, fill = NA),  
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(size = 0.1, color = "grey"),
        panel.grid.major.y = element_line(size = 0.1, color = "grey"),
        axis.line = element_line(size = 0.1, linetype = "solid",
                                 color = "black"),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 10),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))




```

## Cost Plot: Screening, Testing, Treatment (2020 USD) ## 
```{r, echo=FALSE, warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(dev="png")

scr_costs_wk_combo$Type <- "Screening"
test_costs_wk_combo$Type <- "Testing"
tx_costs_wk_combo$Type <- "Treatment"

dat <- rbind(scr_costs_wk_combo,
             test_costs_wk_combo,
             tx_costs_wk_combo, stringsAsFactors = FALSE)

dat_melt <- melt(dat, id.vars = c("Week", "Scenario", "Type"))
colnames(dat_melt)[names(dat_melt) == "variable"] <- "Simulation"
colnames(dat_melt)[names(dat_melt) == "value"] <- "Cost"

total_costs_wk_combo <- ddply(dat_melt, .(Week, Scenario, Simulation), summarize, Cost = sum(Cost))
total_costs_wk_combo$Type <- "Total"

dat_total <- rbind(dat_melt,
             total_costs_wk_combo, stringsAsFactors = FALSE)

dat_melt_mean <- ddply(dat_total, .(Scenario, Type, Week), summarize, Mean = mean(Cost))
dat_melt_cumsum <- ddply(dat_melt_mean, .(Scenario, Type), transform, Cum_Sum = cumsum(Mean))
dat_melt_cumsum$Type <- factor(dat_melt_cumsum$Type, levels = c("Total", "Screening", "Testing", "Treatment"))

b <- ggplot(dat_melt_cumsum, aes(x = Week, y = dat_melt_cumsum$Cum_Sum), alpha = 0.2)
b + geom_line(aes(color = Type, linetype = Scenario)) +
  scale_y_continuous(labels = scales::comma) +
  ylab("Cumulative Costs (2020 USD)") +
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white"),
        panel.border = element_rect(color = "black", size = 0.1, fill = NA),  
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(size = 0.1, color = "grey"),
        panel.grid.major.y = element_line(size = 0.1, color = "grey"),
        axis.line = element_line(size = 0.1, linetype = "solid",
                                 color = "black"),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 10),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))



  
# dat_melt_mean <- dat_melt_mean[which(dat_melt_mean$Week > 2), ]
# 
# c <- ggplot(dat_melt_mean, aes(x = Week, y = dat_melt_mean$Mean), alpha = 0.2)
# c + geom_line(aes(color = Type, linetype = Scenario)) 
#   scale_y_continuous(labels = scales::comma) +
#   ylab("Mean Costs (2020 USD)")
# 

```

## Cost Table: Screening, Testing, Treatment (2020 USD) ## 
```{r, echo=FALSE, warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(dev="png")

calculate_mean_across_sims_costs <- function(cost_file, scenario, type) {
  
  mean_list <- list()
  
  for (year in names(cost_file)) {
    
    dat <- cost_file[[year]]

    mean_CI_dat <- mean_se(dat, mult = 1.96)

    for (column in 1:ncol(mean_CI_dat)) {
      
      mean_CI_dat[, column] <- round(mean_CI_dat[, column], digits = 0)

    }

    mean_CI_dat$Mean_CI <- paste0(mean_CI_dat[, 1], " (", mean_CI_dat[, 2], ", ", mean_CI_dat[, 3], ")")
    mean_CI_dat$Scenario <- scenario
    mean_CI_dat$Type <- type
    
    mean_CI_dat <- mean_CI_dat[, c("Mean_CI", "Scenario", "Type")]
    mean_list[[year]] <- mean_CI_dat
  }
  mean_list_rbind <- do.call(rbind, mean_list)
  mean_list_rbind 
}

run_calc_for_all_costs <- function(base_file, comp_file, type) {
  
  dat_base <- calculate_mean_across_sims_costs(base_file, "Baseline", type)
  dat_comp <- calculate_mean_across_sims_costs(comp_file, "Express", type)
  dat <- rbind(dat_base, dat_comp)
  dat
}

mean_CI_cost_scr <- run_calc_for_all_costs(scr_costs_disc_trad, scr_costs_disc_xpr, "Screening")
mean_CI_cost_test <- run_calc_for_all_costs(test_costs_disc_trad, test_costs_disc_xpr, "Testing")
mean_CI_cost_tx <- run_calc_for_all_costs(tx_costs_disc_trad, tx_costs_disc_xpr, "Treatment")

clean_data_for_table_costs <- function(scr_cost, test_cost, tx_cost) {
  
  combo_data <- data.frame(rbind(scr_cost, test_cost, tx_cost), stringsAsFactors = FALSE)
    combo_data$Year <- rep(c(0:4), nrow(combo_data) / length(0:4))

  combo_data <- dcast(combo_data, Year + Type ~ Scenario, value.var = "Mean_CI")
  combo_data <- combo_data[, c("Type", "Year", "Baseline", "Express")]
  combo_data
}

combo_data <- clean_data_for_table_costs(mean_CI_cost_scr, mean_CI_cost_test, mean_CI_cost_tx)
combo_data <- combo_data[order(combo_data$Type, combo_data$Type), ]
rownames(combo_data) <- c()

kable(combo_data, "latex", booktabs = T) %>% 
  kable_styling(latex_options = c("basic","hover"), position = "left") %>% 
  add_header_above(c(" " = 2, "Mean and 95% CI" = 2)) %>% 
  collapse_rows(columns = 1) 

```

## Cost Bar Plots: Screening, Testing, Treatment (2020 USD) ## 
```{r, echo=FALSE, warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(dev="png")

calculate_mean_across_sims_costs <- function(cost_file, scenario, type) {

  mean_list <- list()

  for (year in names(cost_file)) {

    dat <- cost_file[[year]]

    mean <-mean(dat)
    
    vals <- c(mean, scenario, type)
    mean_list[[year]] <- vals
  }
  
  mean_list_rbind <- data.frame(do.call(rbind, mean_list), stringsAsFactors = FALSE)
  colnames(mean_list_rbind) <- c("Mean", "Scenario", "Type")
  mean_list_rbind$Mean <- as.numeric(mean_list_rbind$Mean)
  mean_list_rbind$Year <- c(0, 1, 2, 3 ,4)
  mean_list_rbind
}

run_calc_for_all_costs <- function(base_file, comp_file, type) {
  
  dat_base <- calculate_mean_across_sims_costs(base_file, "Traditional", type)
  dat_comp <- calculate_mean_across_sims_costs(comp_file, "Express", type)
  dat <- rbind(dat_base, dat_comp)
  dat
}

mean_CI_cost_scr <- run_calc_for_all_costs(scr_costs_disc_trad, scr_costs_disc_xpr, "Screening")
mean_CI_cost_test <- run_calc_for_all_costs(test_costs_disc_trad, test_costs_disc_xpr, "Testing")
mean_CI_cost_tx <- run_calc_for_all_costs(tx_costs_disc_trad, tx_costs_disc_xpr, "Treatment")

combo_data <- data.frame(rbind(mean_CI_cost_scr, mean_CI_cost_test, mean_CI_cost_tx), stringsAsFactors = FALSE)

dat <- combo_data

b <- ggplot(dat, aes(x = Type, y = Mean), alpha = 0.2)
b + geom_col(aes(fill = Scenario), position = position_dodge(0.8), width = 0.7) + 
  facet_wrap(~Year, ncol = 5) +
  scale_y_continuous(labels = scales::comma)
  


```


## Cost-Effectiveness: Cumulative ICER Results (2020 USD) ## 
```{r, echo=FALSE, warning = FALSE, message = FALSE, error = FALSE, results = 'asis'}
knitr::opts_chunk$set(dev="png")

mean_CI_bootstrap_icer_results <- mean_CI_bootstrap_icer_results[c("cost_diff", "inf_avert", "inf_icer", "case_avert", "case_icer")]

clean_data_for_table_icer <- function(icer_results) {
  
  icer_results_formatted <- list()
  
  for (name in names(icer_results)) {
    
    dat <- icer_results[[name]]
    mean_CI_list <- list()
    
    for (column in 1:ncol(dat)) {
      
      dat[, column] <- round(dat[, column], digits = 0)
      icer_results_formatted[[name]] <- dat
    }
    
    dat <- icer_results_formatted[[name]]
    
    for (row in 1:nrow(dat)) {
      
      mean_CI_list[[row]] <- paste0(dat[row, 1], " (", dat[row, 2], ", ", dat[row, 3], ")")
    } 
    
    mean_CI_list_rbind <- do.call(rbind, mean_CI_list)
    icer_results_formatted[[name]] <- mean_CI_list_rbind
    
  }
  icer_results_formatted
}

# combo_data <- clean_data_for_table_icer(mean_CI_bootstrap_icer_results)
# combo_data <- do.call(cbind, combo_data)
# Calculation <- c("(Express - Baseline)", "(Baseline - Express)", "(Cost Diff. / Num. Averted)", "(Baseline - Express)", "(Cost Diff. / Num. Averted)")
# combo_data <- rbind(Calculation, combo_data)
# colnames(combo_data) <- c("Cumul. Cost Difference ", "Cumul. Num. Averted", "Cumul. ICER", "Cumul. Num. Averted", "Cumul. ICER")
# rownames(combo_data) <- c("", 0, 1, 2, 3, 4)
# 
# kable(combo_data, "latex", booktabs = T) %>% 
#   kable_styling(latex_options = c("basic","hover"), position = "left") %>% 
#   add_header_above(c(" " = 2, "Infections (Mean and 95% CI)" = 2, "Cases (Mean and 95% CI)" = 2)) %>% 
#   pack_rows(index = c("Calculation"= 1, "Years" = 5), hline_after = T)

combo_data <- clean_data_for_table_icer(mean_CI_bootstrap_icer_results)
combo_data <- do.call(cbind, combo_data)
colnames(combo_data) <- c("Cumul. Cost Difference ", "Cumul. Num. Averted", "Cumul. ICER", "Cumul. Num. Averted", "Cumul. ICER")
rownames(combo_data) <- as.character(c(1, 2, 3, 4, 5))

kable(combo_data, "latex", booktabs = T) %>% 
  kable_styling(latex_options = c("basic","hover"), position = "left") %>% 
  add_header_above(c(" " = 2, "Infections (Mean and 95% CI)" = 2, "Cases (Mean and 95% CI)" = 2)) %>% 
  pack_rows(index = c("Years" = 5), hline_after = T)

```

## Cost-Effectiveness: Cumulative ICER Results (2020 USD), Sensitivity Analysis Varying Ops Costs ## 
```{r, echo=FALSE, warning = FALSE, message = FALSE, error = FALSE, results = 'asis'}
knitr::opts_chunk$set(dev="png")

prep_sens_analysis_plot <- function(sens_analysis_output, type) {
  
  dat <- sens_analysis_output[which(sens_analysis_output$Type == type), ]
  colnames(dat) <- c("Mean", "CI_Lower", "CI_Upper", "Year", "Base_Level", "Comp_Level", "Type")
  dat$Mean <- round(dat$Mean, digits = 0)
  dat$CI_Lower <- round(dat$CI_Lower, digits = 0)
  dat$CI_Upper <- round(dat$CI_Upper, digits = 0)
  
  dat$Year <- as.character(dat$Year)
  dat[which(dat$Year == "year1"), "Year"] <- 1
  dat[which(dat$Year == "year2"), "Year"] <- 2
  dat[which(dat$Year == "year3"), "Year"] <- 3
  dat[which(dat$Year == "year4"), "Year"] <- 4
  dat[which(dat$Year == "year5"), "Year"] <- 5
  
  dat[which(dat$Type == "inf_icer"), "Type"] <- "Infections"
  dat[which(dat$Type == "case_icer"), "Type"] <- "Cases"
  
  dat
  
}

# types <- unique(mean_CI_bootstrap_icer_results_sens_analysis$Type)

# types <- c("inf_icer", "case_icer")
# 
# for (type in types) {
#   
#   dat <- prep_sens_analysis_plot(mean_CI_bootstrap_icer_results_sens_analysis, type)
#   b <- ggplot(dat, aes(x = Year, y = Mean))
#   
#   b_details <- b + 
#     geom_point(aes(color = Base_Level), position = position_jitter(width = 0.25, height = 0.25)) +
#     scale_y_continuous(labels = scales::comma) +
#     ylab("Mean ICER") +
#    scale_colour_discrete(name = "Express Cost Level", labels = c(paste0(seq(from = 1, to = 10, by = 1), "%")))
#   
#   print(b_details)
# }

# types <- c("inf_icer", "case_icer")

dat_inf <- prep_sens_analysis_plot(mean_CI_bootstrap_icer_results_sens_analysis, "inf_icer")
dat_case <- prep_sens_analysis_plot(mean_CI_bootstrap_icer_results_sens_analysis, "case_icer")
dat <- rbind(dat_inf, dat_case, stringsAsFactors = FALSE)
dat$Comp_Level <- paste0(as.numeric(dat$Comp_Level), "%")
dat$Comp_Level <- factor(dat$Comp_Level, levels = paste0(seq(10, 1, -1), "%"))

b <- ggplot(dat, aes(x = Year, y = Mean))

b + 
  geom_point(aes(color = Comp_Level), position = position_jitter(width = 0.25, height = 0.25)) +
  scale_y_continuous(labels = scales::comma) +
  ylab("Mean ICER") +
  scale_color_viridis(name = "Express Cost Level", discrete = TRUE) +
  # scale_colour_discrete(name = "Express Cost Level", labels = c(paste0(seq(from = 1, to = 10, by = 1), "%"))) +
  facet_wrap(~Type, ncol = 2) +
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white"),
        panel.border = element_rect(color = "black", size = 0.1, fill = NA),  
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(size = 0.1, color = "grey"),
        panel.grid.major.y = element_line(size = 0.1, color = "grey"),
        axis.line = element_line(size = 0.1, linetype = "solid",
                                 color = "black"),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 10),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))


# for (type in types) {
#   
#   dat <- prep_sens_analysis_plot(mean_CI_bootstrap_icer_results_sens_analysis, type)
#   b <- ggplot(dat, aes(x = Comp_Level, y = Mean))
#   
#   b_details <- b + 
#     geom_point(aes(color = Year), position = position_jitter(width = 0.25, height = 0.25)) +
#     ggtitle(type) +
#     scale_y_continuous(labels = scales::comma) +
#     facet_wrap(~ Base_Level, ncol = 5)
#   
#   print(b_details)
#   
# }

# for (type in types) {
#   
#   dat <- prep_sens_analysis_plot(mean_CI_bootstrap_icer_results_sens_analysis, type)
#   b <- ggplot(dat, aes(x = Comp_Level, y = Mean))
#   
#   b_details <- b + 
#     geom_col(aes(fill = Year), position = position_stack()) +
#     ggtitle(type) +
#     scale_y_continuous(labels = scales::comma) +
#     facet_wrap(~ Base_Level, ncol = 5)
#   
#   print(b_details)
#   
# }

```

## Cost-Effectiveness: Cumulative Total Costs Results (2020 USD), Sensitivity Analysis Varying Ops Costs ## 
```{r, echo=FALSE, warning = FALSE, message = FALSE, error = FALSE, results = 'asis'}
knitr::opts_chunk$set(dev="png")

prep_sens_analysis_plot <- function(sens_analysis_output, type) {
  
  dat <- sens_analysis_output[which(sens_analysis_output$Type == type), ]
  colnames(dat) <- c("Mean", "CI_Lower", "CI_Upper", "Year", "Base_Level", "Comp_Level", "Type")
  dat$Mean <- round(dat$Mean, digits = 0)
  dat$CI_Lower <- round(dat$CI_Lower, digits = 0)
  dat$CI_Upper <- round(dat$CI_Upper, digits = 0)
  
  dat$Year <- as.character(dat$Year)
  dat[which(dat$Year == "year1"), "Year"] <- 1
  dat[which(dat$Year == "year2"), "Year"] <- 2
  dat[which(dat$Year == "year3"), "Year"] <- 3
  dat[which(dat$Year == "year4"), "Year"] <- 4
  dat[which(dat$Year == "year5"), "Year"] <- 5
  
  dat[which(dat$Type == "inf_icer"), "Type"] <- "Infections"
  dat[which(dat$Type == "case_icer"), "Type"] <- "Cases"
  
  dat
  
}

# types <- unique(mean_CI_bootstrap_icer_results_sens_analysis$Type)

# types <- c("inf_icer", "case_icer")
# 
# for (type in types) {
#   
#   dat <- prep_sens_analysis_plot(mean_CI_bootstrap_icer_results_sens_analysis, type)
#   b <- ggplot(dat, aes(x = Year, y = Mean))
#   
#   b_details <- b + 
#     geom_point(aes(color = Base_Level), position = position_jitter(width = 0.25, height = 0.25)) +
#     scale_y_continuous(labels = scales::comma) +
#     ylab("Mean ICER") +
#    scale_colour_discrete(name = "Express Cost Level", labels = c(paste0(seq(from = 1, to = 10, by = 1), "%")))
#   
#   print(b_details)
# }

# types <- c("inf_icer", "case_icer")

dat <- prep_sens_analysis_plot(mean_CI_bootstrap_icer_results_sens_analysis, "cost_diff")
# dat_case <- prep_sens_analysis_plot(mean_CI_bootstrap_icer_results_sens_analysis, "cost_diff")
# dat <- rbind(dat_inf, dat_case, stringsAsFactors = FALSE)
dat$Comp_Level <- paste0(as.numeric(dat$Comp_Level), "%")
dat$Comp_Level <- factor(dat$Comp_Level, levels = paste0(seq(10, 1, -1), "%"))

dat[which(dat$Type == "cost_diff"), "Type"] <- "Total Cost Difference"

b <- ggplot(dat, aes(x = Year, y = Mean))

b + 
  geom_point(aes(color = Comp_Level), position = position_jitter(width = 0.25, height = 0.25)) +
  scale_y_continuous(labels = scales::comma) +
  ylab("Mean Total Cost Difference") +
  scale_color_viridis(name = "Express Cost Level", discrete = TRUE) +
  # scale_colour_discrete(name = "Express Cost Level", labels = c(paste0(seq(from = 1, to = 10, by = 1), "%"))) +
  # facet_wrap(~Type, ncol = 2) +
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white"),
        panel.border = element_rect(color = "black", size = 0.1, fill = NA),  
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(size = 0.1, color = "grey"),
        panel.grid.major.y = element_line(size = 0.1, color = "grey"),
        axis.line = element_line(size = 0.1, linetype = "solid",
                                 color = "black"),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 10),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

```

